% !TeX root = proposal.tex

\iffalse

Safety Risks: Please identify the Laboratories in which you will work. 

The Managers of these labs MUST approve the assessment forms you have filled in. 

If you can, try to meet with them and show them the assessments you are planning to post.
The forms are available on Moodle.

Failure Risks: These are your estimates of the risks you face with your current plan. 
If you indicate a high risk of failure, that is, something with which you are uncomfortable, you should outline a new plan to use as backup in case the current plan does not work out for you. 
You can record the details of any alternative plan in your December Interim Report.

\fi

\subsection{Safety Risks}

\newcolumntype{C}{>{\raggedright\arraybackslash}X}
\setlength\extrarowheight{7pt}

\begin{table}[h]
	\centering
	\begin{tabularx}{1\textwidth}{X|X|C|C}
        \textbf{Task} & \textbf{Hazard} & \textbf{Risk} & \textbf{Control} \\ \hline
        \multirow{3}{\hsize}{HDL and NN implementations and programming} & \multirow{3}{\hsize}{Working with a computer} & RSI - \textbf{Low}	& Properly use mouse/keyboard \\ \cline{3-4}
        && 	Eye strain - \textbf{Low} & Make constant breaks\\ \cline{3-4}
        && 	Bad posture - \textbf{Medium} & Make sure to sit properly\\ \hline
        \multirow{3}{\hsize}{Working with the equipment in a lab} 
         & Working with hand tools &  Skin cuts - \textbf{Medium} & Use proper procedure while handling tools \\ \cline{2-4}
         & Accident short-circuits or high power electronics use & Burns from hot wires/chips  - \textbf{Medium}&  Use current limit on power supplies \& appropriate cooling \\\cline{2-4}
         & Public space & COVID-19 infection - \textbf{High}&  Follow all safety procedures suggested by the lab \\
          \hline
\end{tabularx}
	\caption{Risk Assessment Grid}
	\label{table:riskgrid}
\end{table}

\subsection{Failure Risks}

\begin{itemize}
	\item \textbf{Delayed/Cancelled arrival of Ordered goods (FPGA board)}\\
	
	Ordered goods such as the FPGA required for the project may not arrive on time and in such a case an FPGA available to us (DE0 Nano or Xilinx Spartan-6) may be utilized as a substitute. The compromises with choosing a less powerful FPGA should be considered.
	
	\item \textbf{Lack of time to complete all goals of project}
	
	There always exists the risk that a chosen project turns out to be more complex than initially expected. This may result in the project not progressing as quickly as planned and ultimately in the project not being completed in time. If the project should start to fall behind schedule the goals of the project should be altered to allow us to produce a completed system by then end even if it doesn't have all the functionality initially planned.

\end{itemize}