% !TeX root = interim.tex

\iffalse


\fi

\subsection{Difficulties Encountered}

    One of the biggest issues that we encountered was slow training times as the complexity of the neural network grew. This made quick prototyping impossible and slowed down the workflow of the project. Being able to quickly prototype ideas and see how well they perform is key to choosing the optimal architecture/configuration. By discussing this problem with out supervisor we were able to get access to remote servers with GPU's equipped that will speed up the training process.\\
    
    Another reason progress was slower than expected this term was due to other modules having assignment deadlines close to the end of the term. Therefore, progress slowed during the last couple weeks of the term in order for us to focus on assignments. However to make up for this, time will be spent during the holidays to catch up.\\
    
    Finally due to the COVID-19 pandemic meeting up with team members and supervisors for a better collaborative environment has been impossible. This means that we are not able to share ideas or have discussions in person. However meetings and discussion are still being had virtually to make up for this and thus far this has not hindered our progress.

\subsection{Failure Assessment}

    Progress is not so far behind that we have to worry about not being able to complete the project. Rather the most likely cause that we will not be able to progress as quickly as we would like is the acquisition of suitable hardware to implement the designed neural network architecture. The choice of a suitable FPGA and other hardware will be finalized soon. If this FPGA is out of stock or unable to be ordered due to circumstances, an alternative will be chosen with guaranteed availability. Ideally stock that is available in the UK will be chosen as uncertainties with international delivery are higher than usual (due to COVID-19 and brexit). As a last report, the DE0-nano FPGA board with the Cyclone IV FPGA may be utilized, however these boards are not performant enough to meet the requirements of integration with a optical communication channel.\\
    
    The governments decision to enforce tier-4 restrictions on the public means that any non-essential travels are banned. This means that those of us that travelled to family this holiday may not be able to return to campus any time soon. Even though this will not hinder progress greatly, as we have been having meetings virtually anyway, it will mean that we do not have access to the campus at all. As a result we will not be able to inspect or work in the labs until the restrictions are lifted.

\subsection{Updated Safety Risk Assessment}

    As no changes were made to the taken approach, the safety risk assessment remains identical to that discussed in the proposal report \autocite{proposal_report} and can be found in Appendix \ref{table:riskgrid}. 